Evaluating the Supportive Effect of Feature Selection Methods on Machine Learning Models in Monitoring Forest Health Using Hyperspectral Remote Sensing Data

### 2020-04-06 docs/00-manuscripts/ieee/ieee-manuscript.tex
AB-review: wording

Even though the feature selection task was handed over to the filter methods in this study, we ensured to not include features with a pairwise correlation of 1.
Having such can cause undesired effects during model fitting and feature importance calculation.
To account for such, all pair-wise correlations between features were calculated.
For pairs which exceeded the threshold of 0.9999999999 the one with the largest mean absolute correlation was removed.
This process was repeated $p$ times, each time calculating a new correlation matrix.

>>>>

Even though the feature selection step was passed onto the filter methods in this study, we ensured to not include features with a pairwise correlation of 1.
Having such can cause undesired effects during model fitting and feature importance calculation.
To account for such, all pair-wise correlations between features were calculated.
For pairs which exceeded the threshold of 0.9999999999 the one with the largest mean absolute correlation was removed.
This process was repeated $p$ times, each time calculating a new correlation matrix.
